---
title: "P8105 Homework 1"
output: html_document
---

```{r}
library(tidyverse)
```

# Problem 1

Firstly let's load the `penguins` dataset ( after installing package `palmerpenguins`).

```{r}
data("penguins", package = "palmerpenguins")
```

Then let's check what are inside of the dataset:

```{r}
penguins
```

* There are 8 variables, including **species**, **island**, **bill_length_mm**, **bill_depth_mm**, **flipper_length_mm**, **body_mass_g**, **sex**, **year**.

* There are `r nrow(penguins)` rows and `r ncol(penguins)` columns in the dataset.

* The mean flipper length is `r round(mean(penguins$flipper_length_mm, na.rm = TRUE), 2)` mm.

This is going to make a plot! First I generate a dataframe, then use `ggplot` to make a scatterplot.

```{r warning = FALSE}
plot_df =
  tibble(
    x = penguins$bill_length_mm,
    y = penguins$flipper_length_mm
  )

Species = penguins$species

ggplot(plot_df, aes(x = x, y = y, color = Species)) + geom_point()
```

Export the scatterplot:

```{r warning = FALSE}
ggsave("scatter_plot.pdf", height = 4, width = 6)
```

# Problem 2

The chunk below creates a data frame comprised of:
* a random sample of size 10 from a standard Normal distribution
* a logical vector indicating whether elements of the sample are greater than 0
* a character vector of length 10
* a factor vector of length 10, with 3 different factor “levels”

```{r}
p2_df = tibble(
  samp = rnorm(10),
  var_logic = samp > 0,
  var_char = c("a","b","c","b","a","b","c","b","a","b"),
  var_factor = factor(c("Mon","Fri","Sun","Fri","Mon","Fri","Sun","Mon","Fri","Sun"))
)
```

Then I will try to take the mean of each variable in my dataframe.

```{r}
mean(pull(p2_df, samp))
mean(pull(p2_df, var_logic))
mean(pull(p2_df, var_char))
mean(pull(p2_df, var_factor))
```

The means for the random sample and the logical vector worked, but the charactor and the factor vectors did not.

This is going to write a code chunk that applies the `as.numeric` function to the logical, character, and factor variables:

```{r eval=FALSE}
as.numeric(p2_df$var_logic)
as.numeric(p2_df$var_char)
as.numeric(p2_df$var_factor)
```

The logical and factor variables are successfully converted to numeric, but for the charactor variable, it shows _NAs introduced by coercion_ and only NAs are shown in the output.