---
title: "P8105 Homework 1"
output: html_document
---

```{r}
library(tidyverse)
```

# Problem 1

Firstly let's load the `penguins` dataset ( after installing package `palmerpenguins`).

```{r}
data("penguins", package = "palmerpenguins")
```

Then let's check what are inside of the dataset:

```{r}
penguins
```

* There are 8 variables, including **species**, **island**, **bill_length_mm**, **bill_depth_mm**, **flipper_length_mm**, **body_mass_g**, **sex**, **year**.

* There are `r nrow(penguins)` rows and `r ncol(penguins)` columns in the dataset.

* The mean flipper length is `r round(mean(penguins$flipper_length_mm, na.rm = TRUE), 2)` mm.

This is going to make a plot! First I generate a dataframe, then use `ggplot` to make a scatterplot.

```{r warning = FALSE}
plot_df =
  tibble(
    x = penguins$bill_length_mm,
    y = penguins$flipper_length_mm
  )

Species = penguins$species

ggplot(plot_df, aes(x = x, y = y, color = Species)) + geom_point()
```

Export the scatterplot:

```{r warning = FALSE}
ggsave("scatter_plot.pdf", height = 4, width = 6)
```


# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.